Cluster Analysis

### 2020-07-31 MSDS 411 assign 4.Rmd
test

---
title: 'Cluster Analysis'
author: "Nadia Noui-Mehidi"
date: "11/5/2019"
output: rmarkdown::github_document

@@

#states <- read.csv(file="file:///Users/nadianoui-mehidi/Desktop/USStates.csv",head=TRUE,sep=",")
library(NbClust)
library(dplyr)
library(skimr)
library(cluster)
require(tidyverse)
library(kohonen)
require(ggplot2)
require(ggridges)
require(RColorBrewer)
library(vegan)
require(useful)
require(Hmisc)
library(HSAUR)
library(MVA)
library(HSAUR2)
library(fpc)
library(mclust)
library(lattice)
library(car)
library(cluster)
require(maptree)
library(factoextra)
library(data.table)
library(formattable)
library(tidyr)
```

>>>>

---
title: 'Cluster Analysis'
author: "Nadia Noui-Mehidi"
output: rmarkdown::github_document

@@

install.packages("rmarkdown")
#states <- read.csv(file="file:///Users/nadianoui-mehidi/Desktop/USStates.csv",head=TRUE,sep=",")
library(NbClust)
library(dplyr)
library(skimr)
library(cluster)
require(tidyverse)
library(kohonen)
require(ggplot2)
require(ggridges)
require(RColorBrewer)
library(vegan)
require(useful)
require(Hmisc)
library(HSAUR)
library(MVA)
library(HSAUR2)
library(fpc)
library(mclust)
library(lattice)
library(car)
library(cluster)
require(maptree)
library(factoextra)
library(data.table)
library(formattable)
library(tidyr)
```
